### 2016-10-28 writing/paper/sections/meshpatterns.tex
Start coincidences section.
Fix errors in mesh patterns from variable name changes

\begin{definition}
A \emph{mesh pattern} is a pair
\begin{equation*}
    p = (\tau,R)\text{ with } \tau \in \mathfrak{S}_k \text{ and } R \subseteq [0,k]\times [0,k].
\end{equation*}
\end{definition}
We define containment (denoted \(p\preceq \pi\)), and avoidance, of the pattern \(p\) in the permutation
\(\tau\) on mesh patterns analogously to classical containment, and avoidance,
of \(\pi\) in \(\tau\) with the additional restrictions on the relative
position of the occurrence of \(\pi\) in \(\tau\). These restrictions say that
no elements of \(\tau\) are allowed in the regions of the plot corresponding
to shaded boxes in the mesh.

Formally defined by \textcite{journals/combinatorics/BrandenC11},
an \emph{occurrence} of \(p\) in \(\tau\) is a subset \(\omega\) of the plot of
\(\tau, G(\tau) = \{(i,\tau(i)\mid i\in[1,n]\}\) such that there are order-preserving
injections \(\alpha,\beta:[1,k]\mapsto[1,n]\) satisfying the following two conditions.

\noindent Firstly, \(\omega\) is an occurrence of \(\pi\) in the classical sense
  \begin{enumerate}[i.]
    \item \(\omega = \{(\alpha(i),\beta(j)):(i,j)\in G(\pi)\}\)
  \end{enumerate}\saveenum
  Define \(R_{ij} = [\alpha(i)+1,\alpha(i+1)-1]\times[\beta(j)+1,\beta(j+1)-1]\)
   for \(i,j\in[0,k]\) where \(\alpha(0)=\beta(0)=0\) and \(\alpha(k+1)=\beta(k+1)=n+1\). Then
   the second condition is
  \begin{enumerate}[i.]\resetenum
  \item if \((i,j) \in R \text{ then } R_{ij} \cap G(\tau) = \emptyset\)
\end{enumerate}
We call \(R_{ij}\) the region corresponding to \((i,j)\).
We define containment of a mesh pattern \(p\) in another mesh \(\kappa\) as above,
with the additional condition that if \((i,j)\in R\text{ then } R_{ij}\) is
contained in the mesh set of \(\kappa\), in this case we call \(p\) a \emph{subpattern}
of \(\kappa\).

@@

Now we consider the plot for the permutation \(\sigma\). This permutation
avoids \(p\) since for every occurrence of the classical pattern \(\perm{2,1,3}\)
there is at least one point in one of the shaded boxes. For example, consider the
subsequence \(315\) in \(\sigma\), this is an occurrence of \(\perm{2,1,3}\) but
not the mesh pattern since the points with values \(4\) and \(2\) are in the
regions corresponding to the boxes \((0,1)\) and \((0,2)\), which are shaded in
\(p\). This is shown in the plot below.

>>>>

\begin{definition}
A \emph{mesh pattern} is a pair
\begin{equation*}
    p = (\tau,R)\text{ with } \tau \in \mathfrak{S}_k \text{ and } R \subseteq [0,k]\times [0,k].
\end{equation*}
\end{definition}
We define containment (denoted \(p\preceq \pi\)), and avoidance, of the pattern \(p\) in the permutation
\(\pi\) on mesh patterns analogously to classical containment, and avoidance,
of \(\tau\) in \(\pi\) with the additional restrictions on the relative
position of the occurrence of \(\tau\) in \(\pi\). These restrictions say that
no elements of \(\pi\) are allowed in the regions of the plot corresponding
to shaded boxes in the mesh. These boxes are denoted by \(\boks{i,j}\), where the point \((i,j)\) is
the lower left corner of the box.

Formally defined by \textcite{journals/combinatorics/BrandenC11},
an \emph{occurrence} of \(p\) in \(\pi\) is a subset \(\omega\) of the plot of
\(\pi, G(\pi) = \{(i,\pi(i)\mid i\in[1,n]\}\) such that there are order-preserving
injections \(\alpha,\beta:[1,k]\mapsto[1,n]\) satisfying the following two conditions.

\noindent Firstly, \(\omega\) is an occurrence of \(\pi\) in the classical sense
  \begin{enumerate}[i.]
    \item \(\omega = \{(\alpha(i),\beta(j)):(i,j)\in G(\tau)\}\)
  \end{enumerate}\saveenum
  Define \(R_{ij} = [\alpha(i)+1,\alpha(i+1)-1]\times[\beta(j)+1,\beta(j+1)-1]\)
   for \(i,j\in[0,k]\) where \(\alpha(0)=\beta(0)=0\) and \(\alpha(k+1)=\beta(k+1)=n+1\). Then
   the second condition is
  \begin{enumerate}[i.]\resetenum
  \item if \(\boks{i,j} \in R \text{ then } R_{ij} \cap G(\pi) = \emptyset\)
\end{enumerate}
We call \(R_{ij}\) the region corresponding to \(\boks{i,j}\).
We define containment of a mesh pattern \(p\) in another mesh pattern \(q\) as above,
with the additional condition that if \(\boks{i,j}\in R\text{ then } R_{ij}\) is
contained in the mesh set of \(q\), in this case we call \(p\) a \emph{subpattern}
of \(q\).
\begin{definition}
A mesh pattern \(q=(\kappa,T)\) \emph{contains} a mesh pattern \(p=(\tau,R)\) as a \emph{subpattern}
if \(\kappa\) contains \(\tau\) and \(\left(\bigcup_{\boks{i,j}\in R} R_{ij}\right)\subseteq T\).
\end{definition}

@@

Now we consider the plot for the permutation \(\sigma\). This permutation
avoids \(p\) since for every occurrence of the classical pattern \(\perm{2,1,3}\)
there is at least one point in one of the shaded boxes. For example, consider the
subsequence \(315\) in \(\sigma\), this is an occurrence of \(\perm{2,1,3}\) but
not the mesh pattern since the points with values \(4\) and \(2\) are in the
regions corresponding to the boxes \(\boks{0,1}\) and \(\boks{0,2}\), which are shaded in
\(p\). This is shown in the plot below.
